Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
passive to active

Group constants are generated by the modeler with either Serpent
\cite{leppanen_serpent_2015} or SCALE \cite{dehart_reactor_2011}. Moltres 
interpolates group constant temperature dependence from prepared tables, which must be
constructed separately for fuel and moderator regions. For this report,
SCALE-generated group constants were used. To generate the group constants, an
infinite square pitch lattice of cylindrical fuel channels surrounded by
graphite was used, maintaining a fuel fraction of .225 to be consistent with the
\gls{MSRE}. Subsequently, a critical buckling calculation was applied. The SCALE
input files used for generating the group constants can be found in the
\code{io/msre\_conc\_cuboid\_lattice} directory of the
\url{github.com/arfc/scale_io} repository.

@@

Other simulation inputs are outlined in \Cref{table:params}.
The reactor simulation height of 151.75 cm was chosen to produce an
approximately critical reactor configuration corresponding to \gls{BOL}
\gls{MSRE} composition. It is about 10 cm shorter than the actual \gls{MSRE}
height of 162.56 cm.

@@

As described earlier, Moltres runs naturally in parallel. To test its
performance, a scaling study was conducted using a typical 2D axisymmetric input
file. \Cref{fig:scaling_study} shows Moltres's performance. The solution
time follows the ideal closely; slight deviations are expected due to
the expense of communication and the nature of iterative solvers. More
parallelism means the solution process uses more ``older'' information, 
which leads to slower convergence in terms of iterations 
\cite{satish_balay_petsc_2015}.

>>>>

Group constants are generated by the modeler with either Serpent
\cite{leppanen_serpent_2015} or SCALE \cite{dehart_reactor_2011}. Moltres 
interpolates group constant temperature dependence from prepared tables, which must be
constructed separately for fuel and moderator regions. For this report,
we generated group constants with SCALE with
an infinite square pitch lattice of cylindrical fuel channels surrounded by
graphite. This model maintained a fuel fraction of 0.225 to be consistent with the
\gls{MSRE}. Subsequently, a critical buckling calculation was applied. The SCALE
input files used for generating the group constants can be found in the
\code{io/msre\_conc\_cuboid\_lattice} directory of the
\url{github.com/arfc/scale_io} repository.

@@

Other simulation inputs are outlined in \Cref{table:params}.
We chose a reactor simulation height of 151.75 cm to produce an
approximately critical reactor configuration corresponding to \gls{BOL}
\gls{MSRE} composition. This differs from the actual \gls{MSRE} height, which 
was 162.56 cm.

@@

As described earlier, Moltres runs naturally in parallel. To test its
performance, we conducted a scaling study with a typical 2D axisymmetric input
file. \Cref{fig:scaling_study} shows Moltres' performance. The solution
time follows the ideal closely; slight deviations are expected due to
the expense of communication and the nature of iterative solvers. More
parallelism means the solution process uses more ``older'' information, 
which leads to slower convergence in terms of iterations 
\cite{satish_balay_petsc_2015}.
